### 2014-10-22 old_notes/notes_signaling_model_12_11_12.tex
ive added code for tracking mutual information over time and changed figures a bit

\begin{center}
{\bf \LARGE{Development of a Signaling Network}}
\vspace{10pt}
\\ Eleanor Brush
\\ November 01, 2012
\end{center}

@@

%\title{Development of Signaling Network}
%\author{Eleanor Brush}
%\maketitle

\vspace{0pt}
\normalsize
\section{Model as a Stochastic Differential Equation}

@@

\subsection{Evolution of probability distribution over time }
More generally, consider a system
$$ dX_t=a(X_t)dt+\sum_{i=1}^5\sigma_i(X_t)dW_t^{(i)}$$
with $W_t^{(1)},\dots,W_t^{(5)}$ independent Brownian motions.
If $a,\sigma_1,\dots,\sigma_5:\R^2\to\R^2,$ are ``nice" enough functions, and the random variable $X_t$ has a ``nice" enough density function (i.e. $\E[g(X_t)]=\int g(x)p(t,x)dx$ for every bounded measurable function $g$), then according to the Fokker-Planck / Kolmogorov forward equation
\begin{align*}
\frac{\partial p}{\partial t}&=-\sum_{i=1}^2\frac{\partial}{\partial x_i}(a^{(i)}(x)p(t,x))+\frac{1}{2}\sum_{i,j=1}^2\sum_{k=1}^5\frac{\partial^2}{\partial x_i\partial x_j}(\sigma_k^{(i)}\sigma_k^{(j)}p(t,x)
\\ \Rightarrow \frac{\partial p}{\partial t}&=-(m_{e_1}+m_f+b_{s_2}f(x_2))\frac{\partial p}{\partial x_1}-(m_{e_2}-m_f+b_{s_1}f(x_1))\frac{\partial p}{\partial x_2}
\\&+\frac{1}{2}(n_{e_1}^2+n_f^2+b_{s_2}^2f(x_2))\frac{\partial^2 p}{\partial x_1^2}-n_f^2\frac{\partial p}{\partial x_1\partial x_2}+\frac{1}{2}(n_{e_2}^2+n_f^2+b_{s_1}^2f(x_1))\frac{\partial^2 p}{\partial x_2^2}
\end{align*}
using the functions $a$ and $\sigma_i$ as for our particular model.  Note that this requires the function $f:\R\to\R$ be $C^2$.

\subsection{Statistics of the Process WITHOUT Signaling Feedback }
%(See ``The Theory of Stochastic Processes," Cox and Miller.)  Let $p(x_0,x,y_0,y;t)$ be the probability of ending up at $x,y$ at time $t$ given that the process started at $x_0,y_0$.  Then $p$ satisfies the backward equation:
%\begin{align}
%-\frac{\partial}{\partial t}p(x_0,x,y_0,y;t)&=(m_{e_1}+m_f+b_{s_2}f(y_0))\frac{\partial}{\partial x_0}p(x_0,x,y_0,y;t)+(m_{e_1}-m_f+b_{s_2}f(x_0))\frac{\partial}{\partial y_0}p(x_0,x,y_0,y;t) \notag
%\\&+\frac{1}{2}(n_f^2+n_{e_1}^2+b_{s_2}^2f(y_0))\frac{\partial^2}{\partial x_0^2}p(x_0,x,y_0,y;t)+n_f^2\frac{\partial^2}{\partial x_0\partial y_0}p(x_0,x,y_0,y;t) \notag
%\\&+\frac{1}{2}(n_f^2+n_{e_2}^2+b_{s_1}^2f(x_0))\frac{\partial^2}{\partial y_0^2}p(x_0,x,y_0,y;t) \label{back}
%\end{align}
%
%We would like to know the expected time until either estimate reaches the signaling threshold $-T$.  
For simplicity, we start with the case where there is no feedback from signaling to the estimates so that the model becomes
\begin{align*}
dX_t^{(1)}&=\left[m_{e_1}+m_f\right]dt+n_fdW_t^{(1)}+n_{e_1}dW_t^{(2)}
\\ dX_t^{(2)}&=\left[m_{e_2}-m_f\right]dt-n_fdW_t^{(1)}+n_{e_2}dW_t^{(4)}
\end{align*}

This is a simple drift-diffusion model.  We can consider the dynamics of each estimate separately.  We will show results for $X_t^{(1)}$, which follow similarly for $X_t^{(2)}$.  As derived in \cite{Bogacz:2006uq}, the expected time until $X_t^{(1)}$ reaches either $-T$ or $T$ is 
\begin{align*}
\frac{T}{m_e+m_f}\tanh\left(\frac{T(m_e+m_f)}{n_f^2+n_e^2}\right)
\end{align*}
and the probability that $X_t^{(1)}$ reaches $-T$ before it reaches $T$ is
\begin{align*}
\frac{1}{1+\exp\left(\frac{2T(m_e+m_f)}{n_f^2+n_e^2}\right)}
\end{align*}
(assuming $X_t^{(1)}=0$).

The stationary distribution of the estimate will be  (I THINK)
\begin{equation}
X^{(1)}\sim N(\exp((m_{e_1}+m_f)t),\frac{n_f^2+n_e^2}{2}t) \label{ddm_stat}
\end{equation}

\subsection{Ornstein-Uhlenbeck Variant }
As shown in (\ref{ddm_stat}), both the mean and variance of the distribution of estimates increase with time for a pure drift-diffusion model.  The dynamics are more interesting if the estimates don't just keep increasing or decreasing more or less deterministically.  To add negative feedback and prevent this from happening, we can make the size of an error proportional to the current estimate:
\begin{align*}
dX_t^{(1)}&=\left[m_{e_1}X_t^{(1)}+m_f+b_{s_2}f(X_t^{(2)})\right]dt+n_fdW_t^{(1)}+n_{e_1}dW_t^{(2)}+b_{s_2}\sqrt{f(X_t^{(2)})}dW_t^{(3)}
\\ dX_t^{(2)}&=\left[m_{e_2}X_t^{(2)}-m_f+b_{s_1}f(X_t^{(1)})\right]dt-n_fdW_t^{(1)}+n_{e_2}dW_t^{(4)}+b_{s_1}\sqrt{f(X_t^{(1)})}dW_t^{(5)}
\end{align*}
The Fokker-Planck equation now becomes
\begin{align*}
 \frac{\partial p}{\partial t}&=-(m_{e_1}x_1+m_f+b_{s_2}f(x_2))\frac{\partial p}{\partial x_1}-m_{e_1}p-(m_{e_2}x_2-m_f+b_{s_1}f(x_1))\frac{\partial p}{\partial x_2}-m_{e_2}p
\\&+\frac{1}{2}(n_{e_1}^2+n_f^2+b_{s_2}^2f(x_2))\frac{\partial^2 p}{\partial x_1^2}-n_f^2\frac{\partial p}{\partial x_1\partial x_2}+\frac{1}{2}(n_{e_2}^2+n_f^2+b_{s_1}^2f(x_1))\frac{\partial^2 p}{\partial x_2^2}
\end{align*}
If we ignore signaling feedback for the moment and look for a stationary distribution, we want to solve the equation
\begin{align*}
0&=(m_{e_1}x_1+m_f)\frac{\partial p}{\partial x_1}-m_{e_1}p-(m_{e_2}x_2-m_f)\frac{\partial p}{\partial x_2}-m_{e_2}p
\\&+\frac{1}{2}(n_{e_1}^2+n_f^2)\frac{\partial^2 p}{\partial x_1^2}-n_f^2\frac{\partial p}{\partial x_1\partial x_2}+\frac{1}{2}(n_{e_2}^2+n_f^2)\frac{\partial^2 p}{\partial x_2^2}
\\&=(m_ex+m_f)\frac{\partial p}{\partial x}-(m_ey-m_f)\frac{\partial p}{\partial y}-2m_ep+\frac{1}{2}(n_e^2+n_f^2)\frac{\partial^2 p}{\partial x^2}-n_f^2\frac{\partial p}{\partial x\partial y}+\frac{1}{2}(n_e^2+n_f^2)\frac{\partial^2 p}{\partial y^2}
\\& \text{ if we assume $m_{e_1}=m_{e_2}$}
\end{align*}
We can find a stationary distribution for each estimate individually:
\begin{align}
X^{(1)}& \sim N\left(-\frac{m_f}{m_e},\frac{n_f^2+n_e^2}{-2m_e}\right)\ \label{ou_stat1}
\\ \text{ and } X^{(2)} &\sim N\left(\frac{m_f}{m_e},\frac{n_f^2+n_e^2}{-2m_e}\right) \label{ou_stat2}
\end{align}
and the covariance between the two estimates at steady state is
\begin{align*}
Cov(X^{(1)},X^{(2)})=\frac{-n_f^2}{-2m_e}.
\end{align*}

@@

The isoclines of this system are given by
\begin{align*}
\dot{x}=0 \Rightarrow x&=\frac{f}{e}+\frac{b}{e}r(y+T) 
\\\dot{y}=0 \Rightarrow y&=-\frac{f}{e}+\frac{b}{e}r(x+T)
\end{align*}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=1\textwidth]{bifurc_diagram.pdf}
%\end{center}
%\caption{{\bf The equilibria of the signaling model as a function of feedback level, $b$, and signaling threshold, $T$.} For both plots, $e=.5$, $\epsilon=.1$. As $f$ increases from less than $\epsilon e$ to greater than $\epsilon e$, the possible equilibria change.  \label{bifurcation}}
%\end{figure}
%
%\begin{figure}
%\begin{center}
%\includegraphics[width=6in]{heatmap_bifurcation_v1.eps}
%\end{center}
%\caption{{\bf The critical value of the parameter $f$ as a function of $b$ and $T$.}  For a given pair of values of $b$ and $T$, if $f$ is above the value indicated by the heatmap the equilibrium of the system is such that the weaker animal signals at a non-zero rate and the stronger animal doesn't signal.  If $f$ is below the value indicated by the heatmap, the equilibria is as indicated by the text. \label{f_heatmap}}
%\end{figure}
%
%\begin{figure}
%%\includegraphics[]{wireframe_bifurcation_v1.eps}
%\includegraphics[width=\textwidth]{wireframe_bifurcation_v2.eps}
%\caption{{\bf The dependence of the equilibria of the system on all three parameters, $b$, $T$, and $f$.} $T$ is on the $x$ axis, $b$ is on the $y$ axis and $f$ is on the $z$ axis.  If $f$ is above the upper plane, the equilibrium is such that the weaker animal signals at a maximal rate.  If $f$ is between the two planes, the equilibrium is such that the weaker animal signals at a non-zero rate.  If $f$ is below the lower plane, the equilibria depends on $b$ and $T$ as indicated by Figures \ref{bifurcation} and \ref{f_heatmap}. \label{wireframe}}
%\end{figure}

Suppose these dynamics are going on between every pair of animals in a group where the fighting abilities are drawn from some distribution.  How will a network of signals exchanged develop?  Let's first look at a simple metric of such a network: the number of signalers sending signals to a given animal.  
\begin{align*}
P(n \text{ signalers})=\int P(x)P(n \text{ signalers}|x)dx \text{ where $x$ is the fighting ability of a focal animal}
\end{align*}
If $T>\epsilon$ then animal $i$ signals to animal $j$ if and only if $f_j-f_i>e(T-\epsilon)$.  Therefore,
\begin{align*}
P(n \text{ signalers}|x)={N-1 \choose n}P(x-y>e(T-\epsilon))^nP(x-y<e(T-\epsilon))^{(N-1-n)}
\end{align*}
where $N$ is the total number of animals in the group and we use the binomial distribution to express the probability of $n$ signalers as a function of the probability of one of the other $N-1$ animals signaling, which we assume to be independent events.

@@

\begin{figure}
\includegraphics[width=6in]{distributions_of_signals_received_uniform.pdf}
\caption{The probability distribution of number of signalers, assuming a uniform distribution of fighting abilities, as derived in Eq. (\ref{STAR}).  \label{derived_sig_probs}}
\end{figure}

\section{Simulating the Stochastic Process }
A simple updating algorithm allows us to simulate the process as described by the model above (ORNSTEIN-UHLENBECK VARIANT):

\noindent Fix $\Delta t>0$.  Set $t=0$ and initialize $X_0^{(1)}=X_0^{(2)}=0$.

\begin{enumerate}
\item Draw $Z_1,\dots,Z_5$ i.i.d. from $N(0,1)$.
\item \begin{align*}
X_{t+\Delta t}^{(1)}&=X_t^{(1)}+\left(m_{e_1}X_t^{(1)}+m_f+b_{s_2}f(X_t^{(2)}\right)\Delta t+n_f\sqrt{\Delta t}Z_1+n_{e_1}\sqrt{\Delta t}Z_2+b_{s_2}\sqrt{f(X_t^{(2)}}\sqrt{\Delta t}Z_3\\
X_{t+\Delta t}^{(2)}&=X_t^{(2)}+\left(m_{e_2}X_t^{(2)}+m_f+b_{s_1}f(X_t^{(1)}\right)\Delta t+n_f\sqrt{\Delta t}Z_1+n_{e_2}\sqrt{\Delta t}Z_4+b_{s_1}\sqrt{f(X_t^{(1)}}\sqrt{\Delta t}Z_5
\end{align*}
\item $t=t+\Delta t$

To confirm that our simulation is performing reasonably, we let the model run without signaling feedback until the estimates reach stationary distributions and compare these to the analytical prediction, as given by (\ref{ou_stat1}) and (\ref{ou_stat2}).  This comparison is shown in Figure \ref{ou_stat_dist}.  As can be seen in the figure, the observed probability distribution of estimates is statistically indistinguishable from the prediction (for the first, K-S test $D=0.0243$, $p=0.5969$ and for the second, $D=0.0211$, $p=0.766$).

\begin{figure}
\begin{center}
\includegraphics[width=.65\textwidth]{ou_stat_distribution.pdf} \end{center}
\caption{\label{ou_stat_dist} A comparison between the stationary distribution from a simulation of the Ornstein-Uhlenbeck model and the analytically predicted stationary distribution.}
\end{figure}

We are interested in the effect of signaling feedback, i.e. the $b_s$ parameter, on the dynamics of the model.  We run the algorithm $1000$ times so that we obtain, at each point in time, a distribution of each animal's estimates.  We then compare these distributions when there is and isn't signaling.  In both regimes, each animal's estimates reach a relatively stationary distribution fairly quickly so that we can pick a typical time point at which the distributions are not changing any more.  (A Kolmogorov-Smirnov test for the differences between distributions at different points in time does not allow us to reject the null hypothesis that the distributions are the same, at a significance level of $p=0.05$.)  If we allow the simulation to reach a stationary state, we find that the stationary distributions with and without signaling feedback ($b_{s_1}=b_{s_2}=0$ and $b_{s_1}=b_{s_2}\gneq 0$) are quite different for Animal 1(K-S test statistic, $D=0.995,p<2.2\times10^{-16}$), whereas they are statistically indistinguishable for Animal 2 ($D=0.048, p=0.1995$) (Figure (\ref{diff_dists})).

By comparing distributions of the estimates at a given point in time, we compare the behavior of the stochastic process over many realizations.  We can also compare the behavior of individual trajectories over time.  We hypothesize that by increasing the strength of signaling feedback, we should increase the stability of signaling behavior and it should be less likely that the dominant animal's estimate sink to such an extent that it becomes subordinate.  To test this hypothesis, we count, for each run of the simulation, the number of switches between dominance regimes.  A dominance regime is defined by one animal's estimate being below the signaling threshold $-T$ and the other animal's estimate being above the positive threshold $T$.  If a dominance regime is established with Animal $i$'s estimate above the threshold (dominant) and Animal $i+1$'s estimate below the threshold (subordinate) and subsequently a dominance regime is established with Animal $i$ subordinate and Animal $i+1$ dominant, we count this as one switch.  Fixing the other parameters of the model, for each difference in fighting ability $m_f$ and level of signaling feedback $b_{s_1}=b_{s_2}$, we can find the average number of switches that occur in a run of the model.  As the difference in fighting ability increases fewer switches occur since Animal 1 is dominant the vast majority of the time.  Additionally, the average number of switches between dominance regimes decreases as $b_{s}$ increases, and the effect is greater for when the difference in fighting ability is smaller (Figure \ref{diff_switches}).

\begin{figure}
%\begin{subfigure}{.5 \textwidth}
\begin{center}
\includegraphics[width=.85\textwidth]{feedback_estimate_distributions_v2.pdf}
\end{center}
%\caption{}
%\end{subfigure}
\caption{\label{diff_dists} The distribution of estimates for each animal at time $200$, for no signaling feedback and for signaling feedback $b_{s_1}=b_{s_2}=3$.  Other parameters are set as follows: threshold $T=5$, $m_{e_1}=m_{e_2}=-.5$, $n_{e_1}=n_{e_2}=1$, $m_f=5$, $n_f=.5$. }
\end{figure}

\begin{figure}
\begin{subfigure}{1 \textwidth}
\includegraphics[width=.5\textwidth]{feedback_stability_of_dominance_v2.pdf}
\includegraphics[width=.5\textwidth]{feedback_stability_of_dominance_v5.pdf}
\caption{\label{low_error}}
\end{subfigure}
\begin{subfigure}{1 \textwidth}
\includegraphics[width=.5\textwidth]{feedback_stability_of_dominance_v4.pdf}
\caption{\label{high_error}}
\end{subfigure}
%\begin{subfigure}{.5 \textwidth}
%\includegraphics[width=1\textwidth]{feedback_stability_of_dominance_v2.pdf}
%\caption{}
%\end{subfigure}
\caption{\label{diff_switches} The average number of switches between dominance regimes as a function of the difference in fighting ability, $m_f$, between the animals and the degree to which receiving a signal affects an animal's estimate of its dominance, $b_{s_1}=b_{s_2}$.  In general, even for small differences in fighting ability there are very few switches in dominance regimes.  However, fighting ability can be made small enough to allow switches to occur, in which case the strength of signaling feedbacks affects how frequently they happen.  When the leak rate is relatively low, increases in signaling feedback decrease the number of switches (\ref{low_error}).  When the error rate is high / estimates leak back to $0$ very quickly, increasing the signaling feedback actually increases the number of switches between dominance regimes / decreases the stability of a dominance regime (\ref{high_error}).}
\end{figure}

\section{Linear Learning Formulation}

So far, we have considered how the processes of engaging in fights and sending and receiving signals might affect the estimates two animals make of each other's dominance.  We are interested in understanding these processes on the population level and therefore would like to embed these dynamics in a model of a social network.  In order to make this more analytically tractable, we modify our model into a linear learning model and, for the moment, ignore feedback from signaling into the learning process.  Our main question is how the structure of a social network can facilitate individuals' learning about the states of other nodes in the network.

Suppose each individual has a true fighting ability $a_1,\dots,a_N$ and let $f_{jk}=a_j-a_k$.  Consider an individual in a social network observing its own interactions with other members of the group and the interactions between other members of the group and trying to learn each individual's true fighting ability.  Let $x_j(t)$ be the individual's estimate of individual $j$'s fighting ability at time $t$.  The focal individual will be able to learn about other individual's fighting ability by engaging in fights with individuals it interacts with and observing fights between pairs of individuals both of whom it interacts with.  Let 
$$I_{jk}=\left\{
\begin{array}{cccc}
1 & , & \text{ if the focal individual interacts with both $j$ and $k$}\\
0 & , & \text{ otherwise}
\end{array}\right..
$$
Now, $x_j$ will change according to
\begin{align*}
\dot{x}_j(t)&=\sum_kI_{jk}\left[f_{jk}-(x_j(t)-x_k(t))\right] \text{ for } j\lneq N
\\ \text{ and } x_N(t)&=T-\sum_{j\lneq N}x_j(t),
\end{align*}
where we impose a total on the estimates so that they do not diverge.  Therefore,
\begin{align*}
\dot{x}_j(t)&=\sum_{k\neq N}I_{jk}\left[f_{jk}-(x_j(t)-x_k(t))\right]+I_{jN}\left[f_{jN}-(x_j(t)-x_N(t))\right]
\\&=\sum_{k\neq N}I_{jk}\left[f_{jk}-(x_j(t)-x_k(t))\right]+I_{jN}\left[f_{jN}-(x_j(t)-(T-\sum_{k\neq N}x_k(t)))\right]
\\&=\sum_kI_{jk}f_{jk}-x_j(t)\sum_{k}I_{jk}+\sum_{k\neq N}I_{jk}x_k(t)+TI_{jN}-\sum_{k\neq N}I_{jN}x_k(t)
\\&=\sum_kI_{jk}f_{jk}+TI_{jN}-x_j(t)\sum_kI_{jk}+\sum_{k\neq N}(I_{jk}-I_{jN})x_k(t)
\\&=C_j+\sum_{k}L_{jk}x_k(t) \text{ where } C_j=\sum_{k\neq N}I_{jk}f_{jk}+TI_{jN} \text{ and } 
\end{align*}
$L_{jk}$  is an $n-1\times n-1$ matrix given by
$$
L_{jk}=\left\{
\begin{array}{cccc}
-\sum_lI_{jl}+I_{jj}-I_{jN} & , & \text{ if }j=k
\\ I_{jk}-I_{jN} & , & \text{ if } j\neq k
\end{array}\right..
$$
If $x_k(t)=a_k+\frac{T-\sum_ka_k}{N}$  for all $k$, $\dot{x}(t)=0$.  (If $T=\sum_ka_k$ then $x_k(t)=a_k$ is an equilibrium.)

Stability of the equilibrium is determined by the eigenvalues of $L$.

@@

\begin{itemize}
\item More mathematical analysis.
\begin{itemize}
\item We know that if signaling is constantly present or absent, the stationary distribution of the Ornstein-Uhlenbeck process is just shifted and the variance does not change.  However, we do not know what the likelihood of switching from non-signaling to signaling behavior (or vice versa) and whether the estimates would stay in a non-signaling / signaling regime long enough for a stationary distribution to be established.
\end{itemize}
\item Embed the signaling dynamics in a network.  
\begin{itemize}
\item What's the relationship between the distribution of fighting abilities and the distribution of signaling behaviors?  Between fighting abilities and the distribution of power?  And how does that depend on the metric used to calculate power?
\item What's the timescale separation between fighting abilities / fight outcomes / signaling behaviors and the power distribution?  
	\begin{itemize}
	\item when formulated as a Langevin equation: measure timescales through the expected escape time using martingales
	\item when formulated as a dynamical system: measure timescales through time constants of potential wells.
	\end{itemize}
\item What's the / is there a tradeoff between mutual information between fighting abilities and power distribution and stability of the power distribution?
\end{itemize}
\item Compare to data.
	\begin{itemize}
	\item What are the relative rates of fighting and signals observed / predicted?
	\item Can we explain the data with our model?
	\item Do the monkeys weight fights won and lost equally?  Are they trying to maximize reward, minimize punishment, or are the two weighted equally?
	\item Are the monkeys trying to minimize error tae or decision time? Can we tell if they're being forced to signal?
	\item Is there a sense in which the monkeys are performing optimally? 
	\item (ALSO THEORY QUESTION) How efficiently are the monkeys representing /using the information they're observing about the world?
	\item If we can estimate parameters like the thresholds for signaling, how are they related to other variables in the system?
	\end{itemize}
\end{itemize}

>>>>

\begin{center}
{\bf \LARGE{Development of a Signaling Network}}
\vspace{10pt}
\\ Eleanor Brush
\\ updated December 12, 2012
\end{center}

@@

\vspace{0pt}
\normalsize

\section{Motivation }

\begin{table*}\centering
$$\text{The Model : }dX_t=\left(f-eX_t+bf(Y_t)\right)dt+\sigma^2 dW_t^X$$
\ra{1.3}
\begin{tabular}{@{}lll@{}}\toprule
& Behavioral  & Neural 
\\\midrule 
\emph{Objects: } \\
Individual / node & animal & neuron(al population) with preferences
\\ Variable ($X,Y$) & estimate of dominance  & firing rate
\\ Drift ($f$) &  trend in fights  & trend in firing rates
\\ Source of drift & difference in fighting ability & difference in response to stimulus
\\ Leak / error ($e$) & errors in cognitive process & loss of firing activity
\\ Feedback ($b$) & importance of information from other animal & strength of connection between neurons
\\ Threshold ($T$) & estimate below which an animal signals & firing rate at which a decision is made
\\ \midrule
\emph{Interpretation:} \\
Conflict dynamics & fights (and other ways of gathering evidence) & firing rates
\\ Outcome for pair & agreement about which is dominant & agreement about which is firing faster
\\ Outcome for population & signaling network & comparisons between pairs of neurons
\\ Consequence for pair & increased affiliation & ?
\\ Consequence for pop. & power distribution & decision between left and right
\\ \midrule 
\emph{Measure of performance:} \\
For individual & incorrectly signaling, time to decision & 
\\ \bottomrule
\end{tabular}
\caption{Summary of analogy between the model as applied to behavioral and neural systems.}
\end{table*}

\section{Model as a Stochastic Differential Equation}

@@

\subsection{Ornstein-Uhlenbeck Variant }
Both the mean and variance of the distribution of estimates increase with time for a pure drift-diffusion model.  The dynamics are more interesting if the estimates don't just keep increasing or decreasing more or less deterministically.  To add negative feedback and prevent this from happening, we can make the size of an error proportional to the current estimate:
\begin{align*}
dX_t^{(1)}&=\left[m_{e_1}X_t^{(1)}+m_f+b_{s_2}f(X_t^{(2)})\right]dt+n_fdW_t^{(1)}+n_{e_1}dW_t^{(2)}+b_{s_2}\sqrt{f(X_t^{(2)})}dW_t^{(3)}
\\ dX_t^{(2)}&=\left[m_{e_2}X_t^{(2)}-m_f+b_{s_1}f(X_t^{(1)})\right]dt-n_fdW_t^{(1)}+n_{e_2}dW_t^{(4)}+b_{s_1}\sqrt{f(X_t^{(1)})}dW_t^{(5)}
\end{align*}
The Fokker-Planck equation now becomes
\begin{align*}
 \frac{\partial p}{\partial t}&=-(m_{e_1}x_1+m_f+b_{s_2}f(x_2))\frac{\partial p}{\partial x_1}-m_{e_1}p-(m_{e_2}x_2-m_f+b_{s_1}f(x_1))\frac{\partial p}{\partial x_2}-m_{e_2}p
\\&+\frac{1}{2}(n_{e_1}^2+n_f^2+b_{s_2}^2f(x_2))\frac{\partial^2 p}{\partial x_1^2}-n_f^2\frac{\partial p}{\partial x_1\partial x_2}+\frac{1}{2}(n_{e_2}^2+n_f^2+b_{s_1}^2f(x_1))\frac{\partial^2 p}{\partial x_2^2}
\end{align*}
We can find a stationary distribution for each estimate individually:
\begin{align}
X^{(1)}& \sim N\left(-\frac{m_f}{m_e},\frac{n_f^2+n_e^2}{-2m_e}\right)\ \label{ou_stat1}
\\ \text{ and } X^{(2)} &\sim N\left(\frac{m_f}{m_e},\frac{n_f^2+n_e^2}{-2m_e}\right) \label{ou_stat2}
\end{align}
and the covariance between the two estimates at steady state is
\begin{align*}
Cov(X^{(1)},X^{(2)})=\frac{-n_f^2}{-2m_e}.
\end{align*}

@@

\subsection{Equilibria }
The isoclines of this system are given by
\begin{align*}
\dot{x}=0 \Rightarrow x&=\frac{f}{e}+\frac{b}{e}r(y+T) 
\\\dot{y}=0 \Rightarrow y&=-\frac{f}{e}+\frac{b}{e}r(x+T)
\end{align*}

@@

\begin{figure}
\begin{center}
\includegraphics[width=1\textwidth]{bifurc_diagram.pdf}
\end{center}
\caption{{\bf The equilibria of the signaling model as a function of feedback level, $b$, and signaling threshold, $T$.} For both plots, $e=.5$, $\epsilon=.1$. As $f$ increases from less than $\epsilon e$ to greater than $\epsilon e$, the possible equilibria change.  \label{bifurcation}}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=6in]{heatmap_bifurcation_v1.eps}
\end{center}
\caption{{\bf The critical value of the parameter $f$ as a function of $b$ and $T$.}  For a given pair of values of $b$ and $T$, if $f$ is above the value indicated by the heatmap the equilibrium of the system is such that the weaker animal signals at a non-zero rate and the stronger animal doesn't signal.  If $f$ is below the value indicated by the heatmap, the equilibria is as indicated by the text. \label{f_heatmap}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{wireframe_bifurcation_v2.eps}
\caption{{\bf The dependence of the equilibria of the system on all three parameters, $b$, $T$, and $f$.} $T$ is on the $x$ axis, $b$ is on the $y$ axis and $f$ is on the $z$ axis.  If $f$ is above the upper plane, the equilibrium is such that the weaker animal signals at a maximal rate.  If $f$ is between the two planes, the equilibrium is such that the weaker animal signals at a non-zero rate.  If $f$ is below the lower plane, the equilibria depends on $b$ and $T$ as indicated by Figures \ref{bifurcation} and \ref{f_heatmap}. \label{wireframe}}
\end{figure}

\subsection{Development of a Signaling Network }
Suppose these dynamics are going on between every pair of animals in a group where the fighting abilities are drawn from some distribution.  How will a network of signals exchanged develop?  Let's first look at a simple metric of such a network: the number of signalers sending signals to a given animal.  
\begin{align*}
P(n \text{ signalers})=\int P(x)P(n \text{ signalers}|x)dx \text{ where $x$ is the fighting ability of a focal animal}
\end{align*}
If $T>\epsilon$ then animal $i$ signals to animal $j$ if and only if $f_j-f_i>e(T-\epsilon)$.  Therefore,
\begin{align*}
P(n \text{ signalers}|x)={N-1 \choose n}P(x-y>e(T-\epsilon))^nP(x-y<e(T-\epsilon))^{(N-1-n)}
\end{align*}
where $N$ is the total number of animals in the group and we use the binomial distribution to express the probability of $n$ signalers as a function of the probability of one of the other $N-1$ animals signaling, which we assume to be independent events.

@@

\begin{figure}
\includegraphics[width=6in]{distributions_of_signals_received.pdf}
\caption{The probability distribution of number of signalers.  The lines represent the analytically derived distribution Eq. (\ref{STAR}), assuming a uniform distribution of fighting abilities.  The dots represent probabilities from simulated signaling networks where fighting abilities are drawn from a normal distribution. \label{derived_sig_probs}}
\end{figure}

\section{Parameter Optimization for Individuals }
The only case where the parameters really affect the dynamics is when the system exhibits bistability.

\subsection{Minimizing Error Rate or Decision Time }

\subsection{Optimizing Response to Changes in Fighting Ability }

\section{Effects of Individual Optimization on the Signaling Network }

\subsection{Mutual Information between Fight Distribution and Signaling Network }

\subsection{Timescale Separation }

@@

\begin{itemize}
\item More mathematical analysis.
\begin{itemize}
\item expected time for an animal to start signaling
\item probability of one or the other animal to be the first to start signaling
\item optimize error rate / decision time with respect to the threshold for each pair and then see how that affects the resulting distribution of signaling behavior
\end{itemize}
\item Embed the signaling dynamics in a network.  
\begin{itemize}
\item What's the relationship between the distribution of fighting abilities and the distribution of signaling behaviors?  Between fighting abilities and the distribution of power?  And how does that depend on the metric used to calculate power?
\item What's the timescale separation between fighting abilities / fight outcomes / signaling behaviors and the power distribution?  
	\begin{itemize}
	\item when formulated as a Langevin equation: measure timescales through the expected escape time using martingales
	\item when formulated as a dynamical system: measure timescales through time constants of potential wells.
	\end{itemize}
\item What's the / is there a tradeoff between mutual information between fighting abilities and power distribution and stability of the power distribution?
\end{itemize}
\item Compare to data.
	\begin{itemize}
	\item What are the relative rates of fighting and signals observed / predicted?
	\item Can we explain the data with our model?
	\item Do the monkeys weight fights won and lost equally?  Are they trying to maximize reward, minimize punishment, or are the two weighted equally?
	\item Are the monkeys trying to minimize error tae or decision time? Can we tell if they're being forced to signal?
	\item Is there a sense in which the monkeys are performing optimally? 
	\item (ALSO THEORY QUESTION) How efficiently are the monkeys representing /using the information they're observing about the world?
	\item If we can estimate parameters like the thresholds for signaling, how are they related to other variables in the system?
	\end{itemize}
\end{itemize}
